HO unification from object language to meta language

### 2024-03-30 paper/main.tex
bli bla

\newcommand{\occursrigid}{\emph{occurs-rigidly}}
\begin{definition}[\occursrigid]\label{def:occrigid}
  A name $x$ \occursrigid{} in a $\beta$-normal term $t$, if $\forall \rho, x \in
  \subterm{\rho t}$
\end{definition}
In other words $x$ \emph{\occursrigid} in $t$ if it occurs in $t$
outside of the scope of unification variables since an instantiation
is allowed to discard $x$ from the scope of the unification variable.
Note that $\eta$-contraction cannot make $x$ disappear, since the
variables being erased by $\eta$-contraction are locally bound inside $t$.

@@

\noindent
Remark that the converse of \cref{lem:maybeeta} does not hold: 
there exists a term $t \in \maybeeta$
such that forall substitution $\rho$, $\rho t$ is not an
$\eta$-expansion. A simple counter example is
$\lambda x. f \appsep (A \appsep x) \appsep (A \appsep x)$
which is in \maybeeta{} since $x$ does not \occursrigid{} in the first argument
of $f$,
and the second argument of $f$ \reduceto{} $x$. In other words $A \appsep x$
may either use $x$ or discard it.\\
This is however not a problem in the sense that it does not break
\cref{prop:simulation}. Terms in \maybeeta{} are compiled to
unification variables and a link (see \cref{sec:etacomp}):
the link makes progress (see \cref{sec:etaprogress})
in the same step in which the
variable is instantiated, and that compensates for the
potential misclassification.

>>>>

\newcommand{\occursrigid}{\emph{occurs-rigidly}}
\newcommand{\occurrigid}{\emph{occur-rigidly}}
\begin{definition}[\occursrigid]\label{def:occrigid}
  A name $x$ \occursrigid{} in a $\beta$-normal term $t$, if $\forall \rho, x \in
  \subterm{\rho t}$
\end{definition}
In other words $x$ \emph{\occursrigid} in $t$ if it occurs in $t$
outside of the scope of unification variables since an instantiation
is allowed to discard $x$ from the scope of the unification variable.
Note that $\eta$-contraction cannot make $x$ disappear, since the
variables being erased by $\eta$-contraction are locally bound inside $t$.

@@

\noindent
Remark that the converse of \cref{lem:maybeeta} does not hold: 
there exists a term $t \in \maybeeta$
such that forall substitution $\rho$, $\rho t$ is not an
$\eta$-expansion. A simple counter example is
$\lambda x. f \appsep (A \appsep x) \appsep (A \appsep x)$
which is in \maybeeta{} since $x$ does not \occurrigid{} in the first argument
of $f$,
and the second argument of $f$ \reduceto{} $x$. In other words $A \appsep x$
may either use or discard $x$, but our analysis does not know that \emph{the same
term} cannot have two contrasting behaviors.\\
This is however not a problem in the sense that it does not break
\cref{prop:simulation}. Terms in \maybeeta{} are compiled to
unification variables and a link (see \cref{sec:etacomp}):
the link makes progress (see \cref{sec:etaprogress})
in the same step in which the
variable is instantiated, and that compensates for this coarse analysis.
